---
title: 'Workshop Details'
---

```{r setup, include=FALSE}
venue <- "The University of Edinburgh"
address <- "Paterson's Land, The University of Edinburgh, Holyrood Rd, Edinburgh EH8 8AQ"
country <- "gb"      # lowercase two-letter ISO country code such as "fr" (see https://en.wikipedia.org/wiki/ISO_3166-1#Current_codes) for the institution that hosts the workshop
language <- "en"     # lowercase two-letter ISO language code such as "fr" (see https://en.wikipedia.org/wiki/List_of_ISO_639-1_codes) for the workshop
latitude <- "55.94990523657282"        # decimal latitude of workshop venue (use https://www.latlong.net/)
longitude <- "-3.179426294224496"       # decimal longitude of the workshop venue (use https://www.latlong.net)
humandate <- "28 June 2023"    # human-readable dates for the workshop (e.g., "Feb 17-18, 2020")
humantime <- "09:30 - 17:00 BST"    # human-readable times for the workshop e.g., "9:00 am - 4:30 pm CEST (7:00 am - 2:30 pm UTC)"
startdate <- "2023-06-26"      # machine-readable start date for the workshop in YYYY-MM-DD format like 2015-01-01
enddate <- "2023-06-27"        # machine-readable end date for the workshop in YYYY-MM-DD format like 2015-01-02
instructor <- c("Tony Hallam")
helper <- c()
email <- c("support@archer2.ac.uk")
collaborative_notes <- "https://pad.archer2.ac.uk/p/230628-hpc-carpentry"
eventbrite <- NULL           # optional: alphanumeric key for Eventbrite registration, e.g., "1234567890AB" (if Eventbrite is being used)
```

```{r load_config, include=FALSE}
library(yaml)
config <- yaml.load_file("lesson_config.yaml")
```

## Registration

Please use the [ARCHER2 course registration form](https://www.archer2.ac.uk/training/register/?course=230628-hpc-carpentry) to sign up for the workshop.

## General Information

This workshop is an introduction to using high-performance computing systems
effectively. We obviously can't cover every case or give an exhaustive course
on parallel programming in just two days of teaching time. Instead, this
workshop is intended to give students a good introduction and overview of the
tools available and how to use them effectively.

By the end of this workshop, students will know how to:

* Identify problems an HPC system can help solve
* Use the UNIX shell (also known as terminal or command line) to operate a computer,
  connect to an HPC system, and write simple shell scripts.
* Submit and manage jobs on an HPC system using a scheduler, transfer files, and use
  software through environment modules.

This lesson is part of a 3-day ARCHER2 course, you can find the material 
for day 1 at [Introduction to the UNIX shell for High Performance Computing](https://epcced.github.io/2022-07-26-hpc-shell-online/).


## Location

<p id="where">
  <strong>Where:</strong>
  `r address`.
  Get directions with
  <a href="//www.openstreetmap.org/?mlat=`r latitude`&mlon=`r longitude`&zoom=16">OpenStreetMap</a>
  or
  <a href="//maps.google.com/maps?q=`r latitude`,`r longitude`">Google Maps</a>.
</p>

<p id="when"> <strong>When:</strong> `r humandate`. </p>

<p id="requirements">
  <strong>Requirements:</strong>
    Participants must bring a laptop with a
    Mac, Linux, or Windows operating system (not a tablet, Chromebook, etc.) that they have administrative privileges on.

   They should have a few specific software packages installed (listed <a href="#setup">below</a>).
</p>

<p id="accessibility">
  <strong>Accessibility:</strong>
  We are committed to making this workshop
  accessible to everybody.  For workshops at a physical location, the workshop organizers have checked that:
</p>
<ul>
  <li>The room is wheelchair / scooter accessible.</li>
  <li>Accessible restrooms are available.</li>
</ul>
<p>
  Materials will be provided in advance of the workshop and
  large-print handouts are available if needed by notifying the
  organizers in advance.  If we can help making learning easier for
  you (e.g. sign-language interpreters, lactation facilities) please
  get in touch (using contact details below) and we will
  attempt to provide them.
</p>

<p id="contact">
  <strong>Contact:</strong>
  Please email `r email` for more information.
</p>

<p id="roles">
  <strong>Roles:</strong>
  To learn more about the roles at the workshop (who will be doing what),
  refer to <a href="https://carpentries.org/workshop_faq/#what-are-the-roles-of-everyone-participating-in-a-workshop">our Workshop FAQ</a>.
</p>

## Code of Conduct

Everyone who participates in Carpentries activities is required to conform to the 
[Code of Conduct](https://docs.carpentries.org/topic_folders/policies/code-of-conduct.html)

## Collaborative Notes

We will use this [collaborative document](`r collaborative_notes`) for chatting, taking notes, and sharing URLs and bits of code.
